From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-19 Pi+/paper/finite.tex
Change long braid diagram to a fixed set

\[
  \begin{tabular}{m{0.45\linewidth}m{0.1\linewidth}m{0.45\linewidth}}
    \begin{tabular}{m{0.15\linewidth}m{0.05\linewidth}m{0.1\linewidth}}
      \begin{center}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 2,
            thick]
          {braid={1, 1, 1, 1, s_1, 1}};
        \end{tikzpicture}
      \end{center}
       &
      \(\cdots\)
       &
      \begin{center}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 5,
            thick]
          {braid={ s_4, s_3, s_2, s_1, 1, s_4}};
        \end{tikzpicture}
      \end{center}
    \end{tabular}
     &
    \(\xlongrightarrow[]{\longbraid}\)
     &
    \begin{tabular}{m{0.15\linewidth}m{0.05\linewidth}m{0.1\linewidth}}
      \begin{center}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 2,
            thick]
          {braid={1, 1, 1, 1, 1, s_1}};
        \end{tikzpicture}
      \end{center}
       &
      \(\cdots\)
       &
      \begin{center}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 5,
            thick]
          {braid={ s_3, s_4, s_3, s_2, s_1, 1}};
        \end{tikzpicture}
      \end{center}
    \end{tabular}
  \end{tabular}
\]

>>>>

\[
  \begin{tabular}{m{0.4\linewidth}m{0.1\linewidth}m{0.4\linewidth}}
      \begin{center}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 6,
            thick]
          {braid={s_5, s_4, s_3, s_2, s_1, s_5}};
        \end{tikzpicture}
      \end{center}
     &
    \(\xlongrightarrow[]{\longbraid}\)
     &
      \begin{center}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 6,
            thick]
            {braid={s_4, s_5, s_4, s_3, s_2, s_1}};
        \end{tikzpicture}
      \end{center}
  \end{tabular}
\]
